
\title{COMP 354: Diary - Iteration 1}
\author{
        Talar Kochakejian \\
        Student ID: 40018152 \\
        Role: Documenter/Organizer
}
\date{\today}
\setlength{\parindent}{0pt}
\documentclass[12pt]{article}
\begin{document}
\maketitle

\subsection*{Week 1: January 11 - 14}

\begin{itemize}
\item Started reading the group project description.
\item Watched online tutorials to familiarize myself with GitHub.
\end{itemize}

\subsection*{Week 2: January 15 - 21}

\begin{itemize}
\item Went to the tutorial and lab and met my group members, we set a schedule for our upcoming meetings.
\item Brainstormed with team members about the initial structure of our domain model.
\item I created a GitHub repository and pushed an empty java project to the repository and shared it with my teammates so that coders can manage their code with version control
\end{itemize}
\subsection*{Week 3: January 22 - 28}

\begin{itemize}
    \item Read about how to use Latex
    \item Attended the tutorial and lab and the group meeting where we discussed the main scenarios and defined the three main use cases to be implemented by the coders (“AddTransaction”, “ViewTransaction” and “Login”).   
    \item I was assigned the task of documenting parts 5-7 (user groups, functional requirements, non-functional requirements) from the requirements document.
\end{itemize}

\subsection*{Week 4: January 29 - February 4}

\begin{itemize}
    \item Wrote user groups and functional requirements parts of the document.
    \item Wrote non-functional requirements part of the document.
    \item Attended the tutorial, lab and group meeting, we reviewed the first draft of the requirements document and defined the changes and corrections to be applied on the document.
\end{itemize}

\subsection*{Week 5: February 5 - 11}

\begin{itemize}
    \item Made the corrections on my part of the document.
    \item Proofread the final version of the document with group members for iteration one.
    \item I added code changes, meeting minutes and other documents to our GitHub repository.
    \item Attended the tutorial, lab and discussed the next steps to follow for iteration two. 
\end{itemize}

\end{document}